---
title: 'Homework 3'
author: "Snehal Arla"
date: "2/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Due: 2/17/2022 before 11:59pm. Submit in Canvas (file upload).

https://github.com/Snehal2301/practice1-your-Snehal2301

1. Finish the in-class practice in Slides 3-12 in "Lecture 2-2-Practice for git", link: https://yumouqiu.github.io/DS202-Spring2023/Practice/practice01.html  
    a. Download the RMarkdown file with these homework instructions to use as a template for your work. Make sure to replace "Your Name" with your name.  
    b. In the RMarkdown file, write down table of team members, and their github repository links;   
the number of successful pull requests you made, and the github repository to which you requested a change;  
the number of pull requests you accepted, and the github repository from which you accepted.  
    c. Write down a list with at least 3 tips of how to make working with git/github easier  

2. Generate the graph of LifExp vs. gdpPercap for US, Canada (fixed data) and Australia by RMarkdown based on the data set "gapminder-5060", like what we did in the class.  
Please use Github to collaborate on this problem. For example, one member can create the plot of US in his/her repository. The other member will fork this repository, add the result for the second country, and make a pull request for merging into the main repository. Each member should at least analyze one country and make at least one pull request. **Please submit the RMarkdown file, the output file, and the screen shot of the successful pull request and the merge.**

3. Write a paragraph (~200 words) describing an example of what you consider data science. Write your paragraph in R Markdown. Include at least 
    a. one link to a chart or an image and 
    b. at least one itemized or enumerated list.
    

Note: your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. Including the link to the image is the tricky part here. Make sure that you don't use any file structure that depends on your computing environment.


For the submission: submit your solution in an **R Markdown file** and (just for insurance) submit the corresponding html (or Word) file with it. 
gapMinder <- read.csv("gapminder-5060.csv",)
```{r}
gapMinder <- read.csv("gapminder-5060.csv",)
```
```{r}
summary(gapMinder)
```
```{r}
subset_gapMinder <- subset(gapMinder, country %in% c("United States", "Canada", "Australia"))

```


```{r}
library(ggplot2)
ggplot(data = subset_gapMinder, aes(x = lifeExp, y = gdpPercap)) +
  geom_point(aes(color = country))+
   labs(title = "Life Expectancy vs. GDP per capita by Country",
       x = "Life Expectancy",
       y = "GDP per capita") +
  scale_color_manual(values = c("#0072B2", "#D55E00", "#009E73")) +
  scale_x_continuous(limits = c(0, 120)) +
  scale_y_continuous(limits = c(100, 20000))
```

Write down a list with at least 3 tips of how to make working with git/github easier

-It is user friendly, all the features are in simple terms which made it easy for a beginner like me
-Use of forking and pull requests lets you modify the content without modifying the main branch
-Collabration is easy on github, since it is open source and everyone has access to anyones code unless made private



An example that i consider to be of data sciecne took place recently, the covid 19 pandemic data. It is a must that data has to be collected in respect to the pandemic to bring it to a end and rightfully we did from the number of cases and deaths to hospitalization rates and vaccination rates. Data scientists can use this data and make predictions that could potentially decrease the death to covid caqses. A data scinetsist could use the data and make recommendations for the allocation of resources such as hospital beds, ventilators, and vaccines, which was a big factor that was lacking in india.Additionally, they could analyze the impact of various interventions, such as mask mandates or social distancing policies, on the spread of the virus.

https://ourworldindata.org/grapher/cumulative-deaths-and-cases-covid-19

Data scinetists can communciate with any audience at any scale since they have the tools at their disposal,  For example, they can create heat maps that illustrate the concentration of COVID-19 cases by geographic area. They can also use charts to display trends over time, such as the change in vaccination rates in a particular region.

Some examples of COVID-19 data science projects include:

-Developing predictive models for COVID-19 spread and severity
-Analyzing the effectiveness of various public health interventions
-Identifying vulnerable populations and developing strategies to protect them
-Monitoring vaccine distribution and identifying areas where resources are needed most.




