---
title: "Homework 3"
author: "Aditi Nachnani"
date: "2/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Due: 2/17/2022 before 11:59pm. Submit in Canvas (file upload).
1. b. In the RMarkdown file, write down team members, and their github repository links;  
the number of successful pull requests you made, and the github repository to which you requested a change;  
the number of pull requests you accepted, and the github repository from which you accepted.  

Team member names and their github repository links:
- Tara Munjuluri: https://github.com/TaraMunjuluri/practice1-TaraMunjuluri.git
- Snehal Arla: https://github.com/AditiN2003/practice1-Snehal2301.git
- Aditi Nachnani: https://github.com/AditiN2003/practice1-aditin2003.git
 number of pull requests you accepted and number of successful pull requests you made: 2
 github repository to which you requested a change and the github repository from which you accepted: practice1-TaraMunjuluri and practice1-Snehal2301
 
 c. Write down a list with at least 3 tips of how to make working with git/github easier 
 - watch videos on how to work git/github
 - ask friends if lost
 - make sure you make a commit after making a change

2. Generate the graph of LifExp vs. gdpPercap for US, Canada (fixed data) and Australia by RMarkdown based on the data set "gapminder-5060", like what we did in the class.  
```{r}
gapMinder <- read.csv("gapminder-5060.csv")
```
```{r}
summary(gapMinder)
```
```{r}
subset_gapMinder <- subset(gapMinder, country %in% c( "Canada","Australia","United States"))

```


```{r}
library(ggplot2)
ggplot(data = subset_gapMinder, aes(x = lifeExp, y = gdpPercap)) +
  geom_point(aes(color = country))+
   labs(title = "Life Expectancy vs. GDP per capita by Country",
       x = "Life Expectancy",
       y = "GDP per capita") +
  scale_color_manual(values = c("#0072B2", "#D55E00", "#009E73")) +
  scale_x_continuous(limits = c(0, 120)) +
  scale_y_continuous(limits = c(100, 20000))
```

 
 3. Write a paragraph (~200 words) describing an example of what you consider data science. Write your paragraph in R Markdown. Include at least 
    a. one link to a chart or an image and 
    b. at least one itemized or enumerated list.


